Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope

### 2021-10-28 mnras_template.tex
updates

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
\usepackage{indentfirst}
\usepackage{physics}
\usepackage{lineno}
\linenumbers
% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} scheme in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations. By comparing non-calibrated results from the previous work, shear calibration bias can be reduced significantly with \textsc{metacalibration}. Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy. The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases come from, (whether it is the algorithm or detector physics). We incorporate several new updates that are more realistic and necessary to calibrate shear with a better precision relative to the previous version of the simulations. Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$ with the current simulation volume. Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions but consistent with zero for the other direction. This is worse for coadded images. We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem. Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero systematics on relatively undersampled images that \emph{Roman} will produce. In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program. 
\end{abstract}

@@

Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}). Within the dark sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with the same kind are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes, and measuring the distorted shapes describes the gravitational shear field the light passes through. By using millions of these gravitationally lensed galaxies we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually help us learn the history of the development of the structure. For that reason, weak lensing is and will continue to be one of the key probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision. \par

Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}) (include most recent HSC catalog). As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable. Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist & the Science Advisory Team 2010), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the shape measurement on the simulated images, and determine any potential systematic effects and the strategy of mitigating them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (\citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be found in, 
\begin{itemize}
    \item observing strategy
    \item instrumentation effects such as Brighter-Fatter Effect
    \item post-processing pipeline such as image coaddition and object detection
    \item cosmological inference 
\end{itemize}

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. This shear bias arises for various reasons. For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=1$\%$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying this shear bias before the survey is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias. It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending. Tackling the issue of blending is on the way of Y6 DES analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known. One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light of the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image. It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian. It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement.

Recently, Kannawadi et al. (2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations and found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}). They mentioned that his result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters. Regardless of this extended result, we should validate if \textsc{metacalibration} is non-biased with the image simulations specifically made for the \emph{Roman} mission. Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for Roman ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved. \par

@@

\section{Simulations}
\label{sec:sims}
In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented particularly for this work.
\subsection{Simulation Summary}
\label{subsec:imsim}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy.
\begin{itemize}
    \item positions (RA, Dec)
    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
    \item intrinsic galaxy shapes and random orientations
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
    \item artificial gravitational lensing shears
\end{itemize} 
Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).

@@

After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures. These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$. These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512. Once the objects are sorted in MEDS files, we pass them and the corresponding PSF for the SCA to a shape measurement. We pass these multiple exposures with corresponding PSFs to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}). This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.

@@

\subsection{Simulation Updates}
In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic. Along the way to test calibrating shears using \textsc{metacalibration}, we have implemented and made updates to the following parts of the simulation framework. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented the pixel saturation of 100,000 electrons. This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors. 
    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
    In the study by Troxel et al. (2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module. Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias. There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA. Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope. 
    \item \textbf{Single-band and multiband Coadds}: 
    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the potential systematics for an accurate shape measurement. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since by coadding multiple exposures the product is naturally better sampled. Thus, for these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies. We can turn this on and off so that the effect of undersampling is clear. The detailed overview of the coadd process in \texttt{psc} is in Sec. \ref{subsec:psc}. 
    \item \textbf{\textsc{metacalibration} implementation}: We used \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis. \textsc{metacalibration} process takes place after making coadded images, if applicable for the coadd measurements. With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al. (2021) measured. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

@@

\section{Post-catalog Processes}
\label{sec:methods}
Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased. In order to do so, we need to build a measurement pipeline within the simulation framework that contributes to the final measurement. In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.

\subsection{Postage Stamp Coadds}
\label{subsec:psc}
Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object. While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images that are taken with equatorial mount telescopes, which can only move vertically and horizontally, and for images with telescopes that can rotate. When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid. While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the undersampling of the images can be overcome. We describe our coaddition pipeline that is based on \texttt{psc}.

We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files. For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF over the undersampled original PSF. We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane. It will be highly resolved than native pixel scale. For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid. We modified the original code to improve performance of our algorithm, and these modifications are listed below with the general coadding process in \texttt{psc}.

@@

\subsection{Shape measurement with \textsc{metacalibration}}
\label{subsec:mcal}
Once we construct the coadds from the galaxy catalogs to recover the shear signal, we feed them into the \textsc{metacalibration} process. The bootstrapper method in \textsc{ngmix} wraps the \textsc{metacalibration} and the shape fit steps. The priors passed to the fit are listed below.

@@

\section*{Acknowledgements}

>>>>

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
\usepackage{indentfirst}
\usepackage{physics}
\usepackage{lineno}
\linenumbers
\usepackage{ulem}
% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xcolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\normalem
\title[Metacalibration with Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the High-Latitude Imaging Survey Program of the \emph{Roman} Space Telescope}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} in the framework of the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) image simulations. Compared with the non-calibrated results from the previous work, \textsc{metacalibration} can significantly reduce the shear calibration bias. Exploring shear bias is a robust way to test the requirements of the instrument and the overall weak lensing survey strategy. The weak lensing program of \emph{Roman} mission requires the galaxy shapes to be calibrated within about 0.03\%. To reach this goal, we can test our calibration scheme with these simulations and can isolate the sources where these residual shear biases arise. We incorporate \textcolor{red}{several new updates that are more realistic} and necessary to calibrate shear with a better precision relative to the previous version of the simulations. Without the coadditions of the single epoch images, across all three filters we are able to achieve the multiplicative bias of 0.70 per cent within 1.8 $\sigma$. Meanwhile, average additive bias is not consistent with zero due to the strong correlation with the input PSF for one of the spin-2 component directions. This additive bias is worse for the coadded images, while \textcolor{red}{the average multiplicative bias for multiband coadds was xxx}. We find no evidence that shape calibration becomes worse with decreasing image sampling factor based on the Nyquist sampling theorem. Overall, within the current simulation volume, we find that \textsc{metacalibration} can calibrate shapes with zero shear bias on relatively undersampled images that \emph{Roman} will produce. In the future, we will need to substantially increase the simulation volume by 8 to reach the accuracy necessary for the program. 
\end{abstract}

@@

Since the formulation of the physical cosmological model, more observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...633A..69H, 2018PhRvD..98d3528T, 2019PhRvL.122q1301A, 2019PASJ...71...43H, 2021A&A...645A.104A}). Within the sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter which only interacts with non-relativistic matter are responsible for the growth of the large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the region where masses concentrate in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes when observed from the Earth. By detecting millions of these gravitationally lensed galaxies and computing their distortion levels, we can explore the matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually help us learn the history of the development of the large-scale structure in the universe. For that reason, weak lensing is and will continue to be one of the powerful probes in the current and next-decade imaging surveys to constrain cosmological parameters with high precision. \par

Due to the subtlety in the lensing effect and its systematics dominant nature in the “weak” regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we cover more areas in the sky and develop better tools (observatories and algorithms), we find more galaxies and we have already reached to the point where statistical and systematic uncertainties are comparable. Thus, the next-decade legacy surveys, the Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (Euclid Study Scientist \& the Science Advisory Team 2010), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (LSST: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to manage the systematic uncertainties, we must develop realistic image simulations, apply the pre-existing shape measurement on the simulated images, and determine any potential systematic effects and build the strategy of mitigating them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, could occur throughout imaging surveys (e.g., \citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be found in, 
\begin{itemize}
    \item observing strategy
    \item instrumentation effects such as Brighter-Fatter Effect
    \item post-processing pipeline such as image coaddition and object detection
\end{itemize}

In this study, we focus on shear calibration bias, which describes the relationship between gravitational lensing shear and measured galaxy shapes. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$), the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the shear field $\gamma$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below. (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    \gamma^{obs}_{i} = (1+m_{i})\gamma^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $\gamma^{obs}_{i}$ is the two-component observed shear after calibrations and $\gamma^{true}_{i}$ is the true shear. These shear biases arise for various reasons. For space-based surveys, it can be mainly introduced in places such as PSF modelling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as brighter-fatter effect are the potential sources of bias (\citealt{2013MNRAS.429..661M}), where it is shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ (m=0.01), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ would be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying these biases before the real survey is extremely important. \par

Several shear calibration and bias mitigation efforts have been proposed by STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to reduce the significant of shear bias. It has also confirmed that the shear can be calibrated with \textsc{metacalibration} at a-few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending. Tackling the issue of blending is on the way of DES Y6 analysis with the shear-dependent detection and calibration technique (\textsc{metadetect}; \citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} is that it can be directly applied upon real galaxy images, which does not depend on galaxy morphology in simulations, the limitations for future surveys are not well-known. One possible limitation might lie in the effect of the undersampled images, because future space-based surveys like \emph{Euclid} and \emph{Roman} have such a small pixel scale that galaxy images will not be Nyquist sampled at a native resolution (\citealt{2013PASP..125.1496S}) based on the Nyquist-Shannon Sampling Theorem. We define the sampling factor of each filter in \emph{Roman} to be, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in the filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}). The image with the sampling factor, $Q < 2$, is not Nyquist sampled and reffered to as the undersampled image. It is problematic to measure galaxy shapes solely from the undersampled images, because the \emph{Roman} PSF that will be used to recover the shapes is also undersampled and has a complex structure, not simply Gaussian. \textcolor{red}{It is, therefore, necessary to build a robust strategy that can reconstruct better sampled PSF to allow unbiased shape measurement. }

Recently, Kannawadi et al. (2021) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images on \emph{Euclid} image simulations. They found that for \emph{Euclid} mission the shear estimate is biased about 1$\%$ (\citealt{2021MNRAS.502.4048K}). It is mentioned that their result could be extended to the \emph{Roman} mission due to their similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\% for H158 and F184 filters. Regardless of this extended result, we should validate if \textsc{metacalibration} is unbiased with the image simulations specifically made for the \emph{Roman} mission. Our work is based on the image simulation suite of the \emph{Roman} Space Telescope developed by \citet{2021MNRAS.501.2044T}, where we render star and galaxy images from \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). With a few simulation updates and an implementation of \textsc{metacalibration}, we can start to explore if the shear calibration goal of the High-Latitude Survey program for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2019BAAS...51c.341D}) can be achieved. \par

@@

\section{Simulations}
\label{sec:sims}
In this section, we briefly summarize the full simulation details from building a truth catalog to measuring galaxy shapes. Then we describe the simulation updates that are implemented for this work.
\subsection{Simulation Summary}
\label{subsec:imsim}
The base of our image simulations of the \emph{Roman} Space Telescope is the \emph{Roman} simulation suite\footnote{\url{ https://github.com/matroxel/roman_imsim}} developed by \citet{2021MNRAS.501.2044T}, which renders realistic galaxy and star images on 18 Sensor-Chip Assemblies (SCAs) of a 2.5$\times$2.5 deg$^{2}$ patch of the sky provided the observing strategy for the 5-year reference mission and Cycle7 specifications\footnote{\url{https://roman.gsfc.nasa.gov/science/Roman_Reference_Information.html}}. We begin by creating a truth catalog using the simulated galaxy distribution from the Buzzard simulation (\citealt{2019arXiv190102401D}), photometric galaxy catalog sampled from the CANDELS survey (e.g., \citealt{2019ApJ...877..117H}), and Milky Way simulation (Galaxia; \citealt{2011ApJ...730....3S}) for star positions and magnitudes. Then, the following properties are applied to each galaxy.
\begin{itemize}
    \item positions (RA, Dec)
    \item photometries for each \emph{Roman} filter (F184/H158/J129/Y106)
    \item intrinsic galaxy shapes and random orientations
    \item flux ratios of de Vaucouleurs bulge, exponential disk, and star-forming knots
    \item artificial gravitational lensing shears
\end{itemize} 
Within the identical realizations of the simulation, we produce four truth catalogs using four sets of gravitational shears ($e_{1}$, $e_{2}$)=\{(+0.02, 0.00), (-0.02, 0.00), (0.00, +0.02), (0.00, -0.02)\}. This approach helps us to reduce shape and measurement noise when taking the difference in recovered shapes to compute multiplicative bias (\citealt{2019A&A...621A...2P}).

@@

After we generate the object stamps across all the SCAs and pointings, we create Multi-Epoch Data Structure (MEDS) files in which each unique object dictionary contains information of all the exposures. These MEDS files are generated according to the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) of $n_{side}=512$. These MEDS files contain all objects that are located in the area of the sky partitioned according to a HEALPix of $n_{side}$=512. Once the objects are sorted in MEDS files, we pass these multiple exposures with the corresponding PSF to \textsc{ngmix}\footnote{\url{ https://github.com/esheldon/ngmix}} to fit the galaxy shapes with the Gaussian mixture fitting method (\citealt{2014MNRAS.444L..25S}). This shape measurement process produces shape catalogs from which the shear calibration bias can be calculated with \textsc{metacalibration}.

@@

\subsection{Simulation Updates}
In order to accomplish science goals, and build and test the pipelines of weak lensing program in \emph{Roman}, we must keep updating the simulations to be more realistic. We have implemented and made updates to the following parts of the simulation framework to be able to measure unbiased shapes with \textsc{metacalibration}. 
\begin{itemize}
    \setlength\itemsep{1em}
    \item \textbf{Saturation Cuts}:
    We have implemented the pixel saturation of 100,000 electrons. This value is an approximate pixel saturation but in the next generation of the simulations we will use the true saturation from the flight candidate detectors.

    \item \textbf{Rotation of the \emph{Roman} PSF on the sky}:
    In the study by Troxel et al. (2021), the rotations of the \emph{Roman} PSF with respect to the telescope rotation were not engaged properly by \texttt{galsim.roman} module. Since a non-rotating PSF could trigger a preferred direction in the shapes when being deconvolved, we believe that this contributed to the non-zero multiplicative bias result. There has been an update in \texttt{galsim.roman} module to correctly rotate the PSF given the WCS on the SCA. Figure \ref{fig:psfrot} shows a toy PSF of the same pointing but with a different rotation angle of the telescope.

    \item \textbf{Single-band and Multiband Coadds}: 
    We have added and modified the postage stamp coadds (\texttt{psc}) algorithm\footnote{\url{https://github.com/esheldon/psc}} to create coadditions of single-epoch postage stamps. Coadds are usually performed to enhance the signal-to-noise ratio (S/N) of an object and mitigate the measurement noise. If we take advantage of fitting an object in the coadd instead of fitting multiple images of each object in each filter, we can save a factor of 6 in computing time, which is the average number of exposures from the reference survey. Additionally, coadding is one way to reduce the effect of the undersampling of the images since the coadd is naturally better sampled. For these reasons, we must utilize a coadding scheme for the \emph{Roman} galaxies. The detailed overview of the coadd process in \texttt{psc} is in Sec. \ref{subsec:psc}.

    \item \textbf{\textsc{metacalibration} in \textsc{ngmix}}: We implemented \textsc{metacalibration}\footnote{\url{https://github.com/esheldon/ngmix/wiki/Metacalibration}} bootstrapper method, which is a wrapper class to run measurements in the \textsc{ngmix} package and is used extensively to produce weak lensing shape catalog in DES Y3 analysis. \textsc{metacalibration} process takes place after making coadded images. \textsc{ngmix} is able to fit multiple exposures in case for measuring shapes on single-epoch images. With this calibration method, we hope to significantly reduce some of the shear calibration bias Troxel et al. (2021) measured. The detailed overview of \textsc{metacalibration} can be found in Sec.\ref{subsec:mcal}. 
    %\item (Any other changes?)
\end{itemize}

@@

\section{Post-catalog Processes}
\label{sec:methods}
Our goal is to show that the recovered shapes with \textsc{metacalibration} are non-biased. In order to do so, we need to build a measurement pipeline within the current simulation framework that contributes to the final measurement. In this section, we present in detail how coadds are produced with \texttt{psc} from the undersampled single-epoch images, how \textsc{metacalibration} calibrates shapes, and how we measure the shear calibration bias from the \textsc{metacalibration} catalog.

\subsection{Postage Stamp Coadds}
\label{subsec:psc}
Coaddition is the process that reconstructs a Nyquist-sampled image out of multiple exposures of an object. While this process can benefit in increasing the S/N value of an object and reducing the impact of pixel noise, several challenges need to be addressed for images taken with telescopes that can rotate. When the rotation is introduced, this coadding process becomes more complex to interpolate the image to stack pixel grid. While coaddition could introduce systematic bias due to the complexity of the original PSF and its interpolation scheme, the bias with the undersampled images can be overcome \textcolor{red}{by the combinations of the effective coadding process and the careful treatment of the input PSF}. We describe our coaddition pipeline that is based on \texttt{psc}.

We reconstruct the Nyquist-sampled image from multiple exposures in MEDS files. For the coaddition of the PSF, we choose to coadd the image with the oversampled PSF. We oversample the original PSF by a factor of 4 to simulate the better sampled PSF that \emph{Roman} will eventually produce when it constructs the PSF from the full focal plane. It will be highly resolved than native pixel scale. For each exposure of the object we render the \emph{Roman} PSF with a stamp size of 32 pixels at the galaxy centroid, not the image centroid. We modified the original code to improve performance of the \textsc{metacalibration} process later, and these modifications are listed below with the general coadding process in \texttt{psc}.

@@

\subsection{Shape Measurement with \textsc{metacalibration}}
\label{subsec:mcal}
Once we construct the coadds from the galaxy catalogs to recover the shear signal, we feed them into the \textsc{metacalibration} process. The bootstrapper method in \textsc{ngmix} wraps the \textsc{metacalibration} and the shape fit steps. The priors passed to the fit are listed below.

@@

\section{Acknowledgements}
